Milk Intake and Stroke Mortality in the Japan Collaborative Cohort Study---A Bayesian Survival~Analysis

### 2020-09-05 Paperfolder/MDPI_submission/proofreading/nutrients-903270.tex
typos in the affiliation

% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{%
$^{1}$ \quad  Department of Public Health, Aichi Medical University
School of Medicine, 1-1 Yazakokarimata, Nagakute~480-1195,~Aichi,~Japan \\
% $^{2}$ \quad \hl{Department} of Public Health, Aichi Medical University
% School of Medicine, \hl{Nagakute}, Japan; linys@aichi-med-u.ac.jp (Y.L.); tsasa@aichi-med-u.ac.jp (T.S.); ksayo@aichi-med-u.ac.jp (S.K.); kikuchis@aichi-med-u.ac.jp (S.K.)\\
$^{3}$ \quad Departmet of Public Health, Fujita Health University School
of Medicine, Toyoake, Japan; %yatsuya@fujita-hu.ac.jp\\
$^{4}$ \quad Public Health, Department of Social Medicine, Osaka
University Graduate School of Medicine, Osaka, Japan; %iso@pbhel.med.osaka-u.ac.jp\\
$^{5}$ \quad Department of Public Health, Hokkaido University, Faculty
of Medicine, Sapporo, Japan; %tamaa@med.hokudai.ac.jp\\
}
%MDPI: Please check the aff 1 and 2's address. If they are same, please delete one.
%MDPI: Please add the city's post code.
% C.W. the other co-authors did not agree to print all of their email addresses.
% Contact information of the corresponding author
\corres{Correspondence: chaochen@wangcc.me; Tel.: +81-561-62-3311}

>>>>

% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{%
$^{1}$ \quad  Department of Public Health, Aichi Medical University
School of Medicine, 1-1 Yazakokarimata, Nagakute~480-1195,~Aichi,~Japan \\
% $^{2}$ \quad \hl{Department} of Public Health, Aichi Medical University
% School of Medicine, \hl{Nagakute}, Japan; linys@aichi-med-u.ac.jp (Y.L.); tsasa@aichi-med-u.ac.jp (T.S.); ksayo@aichi-med-u.ac.jp (S.K.); kikuchis@aichi-med-u.ac.jp (S.K.)\\
$^{3}$ \quad Department of Public Health, Fujita Health University School
of Medicine, Toyoake, Japan; \\%yatsuya@fujita-hu.ac.jp\\
$^{4}$ \quad Public Health, Department of Social Medicine, Osaka
University Graduate School of Medicine, Osaka, Japan;\\ %iso@pbhel.med.osaka-u.ac.jp\\
$^{5}$ \quad Department of Public Health, Hokkaido University, Faculty
of Medicine, Sapporo, Japan;\\ %tamaa@med.hokudai.ac.jp\\
}
%MDPI: Please check the aff 1 and 2's address. If they are same, please delete one.
%MDPI: Please add the city's post code.
% C.W. the other co-authors did not agree to print all of their email addresses.
% Contact information of the corresponding author
\corres{Correspondence: chaochen@wangcc.me; Tel.: +81-561-62-3311}
